---
title: "homework-number-5"
author: "Maria C. Codlin"
date: "November 18, 2017"
output: html_document
---
##Results

###[1] lm results for entire dataset (reported to 2dp)
Intercept of the model: -9.44, standard error:0.67, confidence interval: -10.77 - -8.11
Slope of the model: 1.04, standard error:0.085, confidence interval: 0.87 - 1.20

###[2] results from sample distribution (to 2dp)
Mean intercept of the model: -9.57, standard error: 1.84, confidence interval: -13.662209 - -6.337821
Mean slope of the model: 1.05, standard error:0.23, confidence interval: 0.61 - 1.54 

The mean intercept and slope of the bootstrapping are very similar to that drawn from the entire dataset, although the standard error and confidence interval are wider. I think this is because the number of samples I took in each bootstrap was relatively small (30), and there were many NAs in the dataset, so there would have been a larger relative variation in the bootstrap datasets. 

## Code
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, stringsAsFactors = FALSE)
```

###Linear model for dataset and confidence intervals
```{r linear model based on entire dataset}
m <- lm(log(d$HomeRange_km2) ~ log(d$Body_mass_female_mean))
summary(m) 
CI<-confint(m, level=0.95)
CI
```

### Sample the data and convert to log
```{r sampling the database}
library(dplyr)
sample_size<-30
s<-NULL
index<-NULL #set up the dummy
m<-NULL
 for (i in 1:1000) {
    index[[i]] <- sample(1:nrow(d), size=sample_size, replace=TRUE)
        s[[i]] <- d[index[[i]],]
        s[[i]] <- select(s[[i]], Body_mass_female_mean, HomeRange_km2)
        s[[i]] <- na.omit(s[[i]])
        s[[i]] <- log(s[[i]])
        m[[i]]<-lm(s[[i]]$HomeRange_km2~s[[i]]$Body_mass_female_mean)
 }
```

### Retrieving slope and intercept data
```{r retrieving slope and intercept data}
intercept<-NULL
slope<-NULL
    for(i in 1:length(m)) {
        intercept[i]  <- summary(m[[i]])$coefficients[1]
        slope[i] <- summary(m[[i]])$coefficients[2]
    }
```

### Stats from the bootstrap
```{r}
mean(intercept)
sd(intercept)
mean(slope)
sd(slope)
quantile(intercept, c(0.025, 0.975))
quantile(slope, c(0.025, 0.975))
```


